### 2019-12-06 README.Rmd
try adding doi badge
try adding doi badge 2
fix image link, rebuild
add workflow description and contributing instructions

@@

>>>>

[![DOI](https://img.shields.io/badge/DOI-10.5063/F16D5R2B-blue.svg)](https://doi.org/10.5063/F16D5R2B)

@@

## Worflow

1. Use the [nesR](https://github.com/jsta/nesR) package to generate the files in [/02_raw_data](/02_raw_data).

2. Hand check the files in [/02_raw_data/merged_data](/02_raw_data/merged_data) against the pdfs in [/01_archival_pdfs](/01_archival_pdfs).

3. Combine files with [05_analysis_scripts/PDF_Merge.R](05_analysis_scripts/PDF_Merge.R).

## Contributing

We've combed the data to try and find all the transciption errors but it's difficult to catch them all. If you find any errors please open an [issue](https://github.com/ReproducibleQM/NES/issues/) or submit a pull request against the files in [/03_qa_data](/03_qa_data).
